---
title: "SBTJ Study 1: Reproducible Analysis"
author: "Nick Tarantino"
output:
  html_document:
    toc: true
    toc_depth: 2
---

This document reproduces the data preparation, models, contrasts, tables, and figures from `SBTJStudy1Markdown_v15.Rmd`. It uses relative paths and plain data-frame output so the package can be run from this folder.

```{r setup, include=FALSE}
library(dplyr)
library(readr)
library(tibble)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)

emm_options(lmer.df = "asymptotic")

output_dir <- "outputs"
figure_dir <- file.path(output_dir, "figures")
dir.create(figure_dir, recursive = TRUE, showWarnings = FALSE)

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.path = paste0(figure_dir, "/"),
  dev = "png",
  dpi = 300
)

fixed_effects_table <- function(model, label) {
  out <- as.data.frame(coef(summary(model)))
  out$term <- rownames(out)
  rownames(out) <- NULL
  out$model <- label
  out[, c("model", "term", setdiff(names(out), c("model", "term")))]
}
```

# 1. Data preparation

The analysis retains target-present trials, applies the documented participant and accuracy exclusions, codes the experimental factors, and joins the selected Qualtrics ratings.

```{r data-preparation}
data_cut <- read_csv("data/data_pilot_raw.csv", show_col_types = FALSE) %>%
  filter(
    trialType == "go",
    !sonaId %in% c("SBTJ-358E01C8", "SBTJ-C05FB0E8")
  ) %>%
  group_by(sonaId) %>%
  filter(!all(is.na(r2))) %>%
  ungroup() %>%
  group_by(sonaId, subBlockId) %>%
  filter(mean(bool_acc, na.rm = TRUE) >= 0.85) %>%
  ungroup() %>%
  group_by(sonaId) %>%
  filter(mean(bool_acc, na.rm = TRUE) >= 0.85) %>%
  ungroup()

quad_levels <- c("lower_left", "lower_right", "upper_left", "upper_right")

df <- data_cut %>%
  mutate(
    graph = case_when(
      grepl("bar", subBlockId, ignore.case = TRUE) ~ "bar",
      grepl("scatter", subBlockId, ignore.case = TRUE) ~ "scatter",
      TRUE ~ NA_character_
    ),
    graph = factor(graph, levels = c("bar", "scatter")),
    direction = case_when(
      grepl("pos", subBlockId, ignore.case = TRUE) ~ "pos",
      grepl("neg", subBlockId, ignore.case = TRUE) ~ "neg",
      TRUE ~ NA_character_
    ),
    direction = factor(direction, levels = c("neg", "pos")),
    targetQuadrant = factor(targetQuadrant, levels = quad_levels),
    regression_slope = as.numeric(regression_slope),
    abs_slope = abs(regression_slope),
    abs_slope_c = abs_slope - mean(abs_slope, na.rm = TRUE),
    accuracy2 = as.integer(bool_acc),
    math_level = case_when(
      Q2 %in% c("Geometry", "Algebra", "Pre-calculus") ~ "below_calc",
      Q2 == "1 semester of calculus" ~ "calc_1",
      Q2 == "2 semesters of calculus" ~ "calc_2",
      Q2 == "Beyond 2 semesters of calculus" ~ "calc_2plus",
      !is.na(Q2) & trimws(Q2) != "" ~ "calc_1",
      TRUE ~ NA_character_
    ),
    math_level = factor(
      math_level,
      levels = c("below_calc", "calc_1", "calc_2", "calc_2plus"),
      ordered = TRUE
    ),
    math_num = as.numeric(math_level),
    math_c = math_num - mean(math_num, na.rm = TRUE),
    graph_c = case_when(
      graph == "bar" ~ -0.5,
      graph == "scatter" ~ 0.5,
      TRUE ~ NA_real_
    ),
    direction_c = case_when(
      direction == "neg" ~ -0.5,
      direction == "pos" ~ 0.5,
      TRUE ~ NA_real_
    )
  )

df_rt <- df %>%
  filter(
    accuracy2 == 1,
    responseTime >= 250,
    responseTime <= 3000
  ) %>%
  mutate(
    targetQuadrant = factor(targetQuadrant, levels = quad_levels),
    log_rt = log(responseTime),
    parrott_incompatible = case_when(
      graph == "bar" & direction == "pos" & targetQuadrant == "upper_left" ~ 1,
      graph == "bar" & direction == "neg" & targetQuadrant == "upper_right" ~ 1,
      graph == "scatter" & direction == "pos" & targetQuadrant == "lower_right" ~ 1,
      graph == "scatter" & direction == "neg" & targetQuadrant == "upper_right" ~ 1,
      TRUE ~ 0
    ),
    compatibility_c = if_else(parrott_incompatible == 1, 0.5, -0.5)
  )

qualtrics_vars <- read_csv(
  "data/Thesis_Pilot_QualtricsDataFinal.csv",
  show_col_types = FALSE
) %>%
  select(ResponseId, Q23_1, Q23_2, Q23_4, Q23_8, Q23_9, Q23_10)

df <- df %>%
  left_join(qualtrics_vars, by = c("qualtricsResponseId" = "ResponseId"))

df_rt <- df_rt %>%
  left_join(qualtrics_vars, by = c("qualtricsResponseId" = "ResponseId"))

data_summary <- tibble(
  retained_participants = n_distinct(df_rt$sonaId),
  retained_rt_trials = nrow(df_rt),
  mean_rt_ms = mean(df_rt$responseTime, na.rm = TRUE),
  sd_rt_ms = sd(df_rt$responseTime, na.rm = TRUE),
  sd_centered_math_experience = sd(df_rt$math_c, na.rm = TRUE)
)
write_csv(data_summary, file.path(output_dir, "data_summary.csv"))
data_summary
```

# 2. Incompatible-quadrant models

Four models test the predicted incompatible quadrant separately for each graph-type-by-direction cell.

```{r incompatible-quadrant-models}
C_tq_UL <- structure(
  cbind(
    UL_vs_Rest = c(-1/3, -1/3, 1, -1/3),
    LR_vs_LL = c(-0.5, 0.5, 0, 0),
    UR_vs_Lower = c(-1/3, -1/3, 0, 2/3)
  ),
  dimnames = list(quad_levels, c("UL_vs_Rest", "LR_vs_LL", "UR_vs_Lower"))
)

C_tq_UR <- structure(
  cbind(
    UR_vs_Rest = c(-1/3, -1/3, -1/3, 1),
    LR_vs_LL = c(-0.5, 0.5, 0, 0),
    UL_vs_Lower = c(-1/3, -1/3, 2/3, 0)
  ),
  dimnames = list(quad_levels, c("UR_vs_Rest", "LR_vs_LL", "UL_vs_Lower"))
)

C_tq_LR <- structure(
  cbind(
    LR_vs_Rest = c(-1/3, 1, -1/3, -1/3),
    LL_vs_UL = c(-0.5, 0, 0.5, 0),
    UR_vs_LL_UL_avg = c(-1/3, 0, -1/3, 2/3)
  ),
  dimnames = list(quad_levels, c("LR_vs_Rest", "LL_vs_UL", "UR_vs_LL_UL_avg"))
)

fit_cell <- function(data, contrast_matrix) {
  data <- droplevels(data)
  contrasts(data$targetQuadrant) <- contrast_matrix
  lmer(
    log_rt ~ targetQuadrant + (1 + targetQuadrant | sonaId),
    data = data,
    REML = FALSE
  )
}

m_bar_pos_UL <- fit_cell(
  filter(df_rt, graph == "bar", direction == "pos"), C_tq_UL
)
m_bar_neg_UR <- fit_cell(
  filter(df_rt, graph == "bar", direction == "neg"), C_tq_UR
)
m_scatter_pos_LR <- fit_cell(
  filter(df_rt, graph == "scatter", direction == "pos"), C_tq_LR
)
m_scatter_neg_UR <- fit_cell(
  filter(df_rt, graph == "scatter", direction == "neg"), C_tq_UR
)

cell_model_results <- bind_rows(
  fixed_effects_table(m_bar_pos_UL, "bar_increasing"),
  fixed_effects_table(m_bar_neg_UR, "bar_decreasing"),
  fixed_effects_table(m_scatter_pos_LR, "scatter_increasing"),
  fixed_effects_table(m_scatter_neg_UR, "scatter_decreasing")
)
write_csv(cell_model_results, file.path(output_dir, "incompatible_quadrant_models.csv"))
writeLines(
  c(
    "BAR, INCREASING", capture.output(summary(m_bar_pos_UL)),
    "", "BAR, DECREASING", capture.output(summary(m_bar_neg_UR)),
    "", "SCATTER, INCREASING", capture.output(summary(m_scatter_pos_LR)),
    "", "SCATTER, DECREASING", capture.output(summary(m_scatter_neg_UR))
  ),
  file.path(output_dir, "incompatible_quadrant_model_summaries.txt")
)
cell_model_results
```

# 3. Dimensional and graph-within-graph model

The quadrant factor is represented by vertical, horizontal, and diagonal orthogonal contrasts.

```{r dimensional-model}
C_tq <- structure(
  cbind(
    Vertical = c(-0.5, -0.5, 0.5, 0.5),
    Horizontal = c(-0.5, 0.5, -0.5, 0.5),
    Diagonal = c(0.5, -0.5, -0.5, 0.5)
  ),
  dimnames = list(quad_levels, c("Vertical", "Horizontal", "Diagonal"))
)

contrasts(df_rt$targetQuadrant) <- C_tq

m_dimensional_full <- lmer(
  log_rt ~ targetQuadrant * direction_c * graph_c + abs_slope_c +
    (1 + direction_c + graph_c || sonaId),
  data = df_rt,
  REML = FALSE
)

dimensional_fixed <- fixed_effects_table(m_dimensional_full, "dimensional")
write_csv(dimensional_fixed, file.path(output_dir, "dimensional_model_fixed_effects.csv"))
writeLines(
  capture.output(summary(m_dimensional_full)),
  file.path(output_dir, "dimensional_model_summary.txt")
)
dimensional_fixed
```

## 3.1 Simple vertical and horizontal effects

```{r dimensional-simple-effects}
emm_dir_graph <- emmeans(
  m_dimensional_full,
  ~ targetQuadrant | direction_c * graph_c,
  at = list(
    direction_c = c(-0.5, 0.5),
    graph_c = c(-0.5, 0.5),
    abs_slope_c = 0
  )
)

simple_dir_graph <- contrast(
  emm_dir_graph,
  method = list(
    Vertical = c(-0.5, -0.5, 0.5, 0.5),
    Horizontal = c(-0.5, 0.5, -0.5, 0.5)
  ),
  by = c("direction_c", "graph_c")
)

simple_dir_graph_tab <- as.data.frame(
  summary(simple_dir_graph, infer = c(TRUE, TRUE))
)
simple_dir_graph_tab$p.bonferroni <- ave(
  simple_dir_graph_tab$p.value,
  simple_dir_graph_tab$contrast,
  simple_dir_graph_tab$direction_c,
  FUN = function(p) p.adjust(p, method = "bonferroni")
)
write_csv(simple_dir_graph_tab, file.path(output_dir, "dimensional_simple_effects.csv"))
simple_dir_graph_tab
```

## 3.2 Contrasts across trend direction

```{r dimensional-direction-contrasts}
vert_by_dir_graph <- contrast(
  emm_dir_graph,
  method = list(Vertical = c(-0.5, -0.5, 0.5, 0.5)),
  by = c("direction_c", "graph_c")
)

horiz_by_dir_graph <- contrast(
  emm_dir_graph,
  method = list(Horizontal = c(-0.5, 0.5, -0.5, 0.5)),
  by = c("direction_c", "graph_c")
)

bonf_across_graph <- function(x) {
  out <- as.data.frame(summary(x))
  group <- if ("contrast" %in% names(out)) out$contrast else rep(1L, nrow(out))
  out$p.bonferroni <- ave(
    out$p.value,
    group,
    FUN = function(p) p.adjust(p, method = "bonferroni")
  )
  out
}

vertical_direction_tab <- bonf_across_graph(
  pairs(vert_by_dir_graph, simple = "direction_c")
)
horizontal_direction_tab <- bonf_across_graph(
  pairs(horiz_by_dir_graph, simple = "direction_c")
)

write_csv(
  vertical_direction_tab,
  file.path(output_dir, "vertical_contrast_across_direction.csv")
)
write_csv(
  horizontal_direction_tab,
  file.path(output_dir, "horizontal_contrast_across_direction.csv")
)

vertical_direction_tab
horizontal_direction_tab
```

## 3.3 Diagonal contrast

```{r diagonal-contrast}
emm_dir <- emmeans(
  m_dimensional_full,
  ~ targetQuadrant | direction_c,
  at = list(
    direction_c = c(-0.5, 0.5),
    graph_c = c(-0.5, 0.5),
    abs_slope_c = 0
  )
)

diag_by_dir <- contrast(
  emm_dir,
  method = list(Diagonal = c(0.5, -0.5, -0.5, 0.5)),
  by = "direction_c"
)

diagonal_tab <- as.data.frame(summary(diag_by_dir, infer = c(TRUE, TRUE)))
write_csv(diagonal_tab, file.path(output_dir, "diagonal_contrast.csv"))
diagonal_tab
```

## 3.4 Dimensional figures

```{r dimensional-figure-functions}
tidy_ms <- function(x) {
  out <- as.data.frame(summary(x, infer = c(TRUE, FALSE)))
  names(out)[names(out) %in% c("asymp.LCL", "lower.CL")] <- "lcl"
  names(out)[names(out) %in% c("asymp.UCL", "upper.CL")] <- "ucl"
  out$rt <- exp(out$estimate)
  out$lo <- exp(out$lcl)
  out$hi <- exp(out$ucl)
  out$Direction <- factor(
    ifelse(out$direction_c > 0, "Increasing", "Decreasing"),
    levels = c("Decreasing", "Increasing")
  )
  if ("graph_c" %in% names(out)) {
    out$Graph <- factor(
      ifelse(out$graph_c > 0, "Scatter", "Bar"),
      levels = c("Bar", "Scatter")
    )
  }
  out
}

bias_plot <- function(data, x_label) {
  ggplot(data, aes(Position, rt, colour = Direction, group = Direction)) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.6) +
    geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.08, linewidth = 0.6) +
    scale_y_continuous(breaks = scales::breaks_width(50)) +
    labs(x = x_label, y = "Estimated reaction time (ms)") +
    theme_bw(base_size = 12)
}
```

```{r vertical-position-figure, fig.width=6.5, fig.height=3.5}
vertical_cells <- tidy_ms(contrast(
  emm_dir_graph,
  method = list(Lower = c(0.5, 0.5, 0, 0), Upper = c(0, 0, 0.5, 0.5)),
  by = c("direction_c", "graph_c")
))
vertical_cells$Position <- factor(vertical_cells$contrast, levels = c("Lower", "Upper"))
vertical_plot <- bias_plot(vertical_cells, "Vertical target position") + facet_wrap(~ Graph)
vertical_plot
```

```{r horizontal-position-figure, fig.width=6.5, fig.height=3.5}
horizontal_cells <- tidy_ms(contrast(
  emm_dir_graph,
  method = list(Left = c(0.5, 0, 0.5, 0), Right = c(0, 0.5, 0, 0.5)),
  by = c("direction_c", "graph_c")
))
horizontal_cells$Position <- factor(horizontal_cells$contrast, levels = c("Left", "Right"))
horizontal_plot <- bias_plot(horizontal_cells, "Horizontal target position") + facet_wrap(~ Graph)
horizontal_plot
```

```{r diagonal-position-figure, fig.width=4.5, fig.height=3.5}
diagonal_cells <- tidy_ms(contrast(
  emm_dir,
  method = list(`LR+UL` = c(0, 0.5, 0.5, 0), `LL+UR` = c(0.5, 0, 0, 0.5)),
  by = "direction_c"
))
diagonal_cells$Position <- factor(diagonal_cells$contrast, levels = c("LR+UL", "LL+UR"))
diagonal_plot <- bias_plot(diagonal_cells, "Diagonal target position")
diagonal_plot
```

# 4. Model comparison

The reduced incompatible-quadrant model is compared with the dimensional model using maximum likelihood, AIC, BIC, and a likelihood-ratio test.

```{r model-comparison}
m_parrott_full <- lmer(
  log_rt ~ compatibility_c + graph_c * direction_c + abs_slope_c +
    (1 + direction_c + graph_c || sonaId),
  data = df_rt,
  REML = FALSE
)

stopifnot(nobs(m_parrott_full) == nobs(m_dimensional_full))

parrott_fixed <- fixed_effects_table(m_parrott_full, "incompatible_quadrant")
model_comparison <- as.data.frame(anova(m_parrott_full, m_dimensional_full))
model_comparison$model <- rownames(model_comparison)
rownames(model_comparison) <- NULL
model_comparison <- model_comparison[, c("model", setdiff(names(model_comparison), "model"))]

write_csv(parrott_fixed, file.path(output_dir, "incompatible_full_model_fixed_effects.csv"))
write_csv(model_comparison, file.path(output_dir, "model_comparison.csv"))
writeLines(
  capture.output(summary(m_parrott_full)),
  file.path(output_dir, "incompatible_full_model_summary.txt")
)

parrott_fixed
model_comparison
```

# 5. Graph-experience moderation

Three models reproduce the bar-rating-only, scatter-rating-only, and combined-rating analyses.

```{r experience-models}
df_rt <- df_rt %>%
  mutate(
    q23_2_c = Q23_2 - mean(Q23_2, na.rm = TRUE),
    q23_4_c = Q23_4 - mean(Q23_4, na.rm = TRUE),
    q23_10_c = Q23_10 - mean(Q23_10, na.rm = TRUE)
  )

sd_q23_2 <- sd(df_rt$q23_2_c, na.rm = TRUE)
sd_q23_4 <- sd(df_rt$q23_4_c, na.rm = TRUE)

random_effects <- "(1 + graph_c + direction_c || sonaId)"

fit_dim <- function(focal, controls = character(0)) {
  terms <- c(
    sprintf("targetQuadrant * direction_c * graph_c * %s", focal),
    sprintf("targetQuadrant * direction_c * graph_c * %s", controls),
    "abs_slope_c",
    random_effects
  )
  formula <- as.formula(paste("log_rt ~", paste(terms, collapse = " + ")))
  lmer(formula, data = df_rt, REML = FALSE)
}

m_bar_rating <- fit_dim("q23_2_c")
m_scat_rating <- fit_dim("q23_4_c")
m_full <- fit_dim("q23_2_c", c("q23_4_c", "q23_10_c"))

experience_model_n <- tibble(
  model = c("bar_rating", "scatter_rating", "combined"),
  participants = c(
    as.integer(ngrps(m_bar_rating)["sonaId"]),
    as.integer(ngrps(m_scat_rating)["sonaId"]),
    as.integer(ngrps(m_full)["sonaId"])
  )
)
write_csv(experience_model_n, file.path(output_dir, "experience_model_sample_sizes.csv"))
experience_model_n
```

## 5.1 Moderation contrasts

```{r moderation-contrasts}
extract_mod <- function(model, moderator, moderator_sd, model_label) {
  model_variables <- all.vars(formula(model))
  at <- list(
    direction_c = c(-0.5, 0.5),
    graph_c = c(-0.5, 0.5),
    abs_slope_c = 0
  )
  at[[moderator]] <- c(-moderator_sd, moderator_sd)
  for (variable in c("q23_2_c", "q23_4_c", "q23_10_c", "math_c")) {
    if (variable != moderator && variable %in% model_variables) at[[variable]] <- 0
  }

  emm <- emmeans(
    model,
    as.formula(paste("~ targetQuadrant | direction_c * graph_c *", moderator)),
    at = at
  )

  grab <- function(weights, label) {
    contrast_grid <- contrast(
      emm,
      method = setNames(list(weights), label),
      by = c("direction_c", "graph_c", moderator)
    )
    out <- as.data.frame(
      summary(pairs(pairs(contrast_grid, simple = "direction_c"), simple = moderator))
    )
    statistic <- if ("t.ratio" %in% names(out)) out$t.ratio else out$z.ratio
    data.frame(
      Model = model_label,
      Contrast = label,
      Graph = ifelse(out$graph_c > 0, "Scatter", "Bar"),
      Estimate = out$estimate,
      SE = out$SE,
      statistic = statistic,
      p = out$p.value,
      stringsAsFactors = FALSE
    )
  }

  out <- bind_rows(
    grab(c(-0.5, -0.5, 0.5, 0.5), "Vertical"),
    grab(c(-0.5, 0.5, -0.5, 0.5), "Horizontal"),
    grab(c(0.5, -0.5, -0.5, 0.5), "Diagonal")
  )
  out$p_bonferroni <- ave(
    out$p,
    out$Contrast,
    FUN = function(p) p.adjust(p, method = "bonferroni")
  )
  out
}

bar_moderation <- bind_rows(
  extract_mod(m_bar_rating, "q23_2_c", sd_q23_2, "focal_rating_alone"),
  extract_mod(m_full, "q23_2_c", sd_q23_2, "combined_model")
)

scatter_moderation <- bind_rows(
  extract_mod(m_scat_rating, "q23_4_c", sd_q23_4, "focal_rating_alone"),
  extract_mod(m_full, "q23_4_c", sd_q23_4, "combined_model")
)

write_csv(bar_moderation, file.path(output_dir, "bar_rating_moderation.csv"))
write_csv(scatter_moderation, file.path(output_dir, "scatter_rating_moderation.csv"))

bar_moderation
scatter_moderation
```

## 5.2 Simple effects by rating

```{r rating-simple-effects}
rating_simple <- function(moderator, moderator_sd, graph_keep) {
  at <- list(direction_c = c(-0.5, 0.5), graph_c = c(-0.5, 0.5), abs_slope_c = 0)
  at[[moderator]] <- c(-moderator_sd, moderator_sd)
  for (variable in c("q23_2_c", "q23_4_c", "q23_10_c")) {
    if (variable != moderator) at[[variable]] <- 0
  }

  emm <- emmeans(
    m_full,
    as.formula(paste("~ targetQuadrant | direction_c * graph_c *", moderator)),
    at = at
  )

  contrasts_by_cell <- contrast(
    emm,
    method = list(
      Vertical = c(-0.5, -0.5, 0.5, 0.5),
      Horizontal = c(-0.5, 0.5, -0.5, 0.5)
    ),
    by = c("direction_c", "graph_c", moderator)
  )

  out <- as.data.frame(summary(contrasts_by_cell, infer = c(TRUE, TRUE)))
  out <- out[out$graph_c == graph_keep, ]
  out$rating_variable <- moderator
  out
}

rating_simple_all <- bind_rows(
  rating_simple("q23_2_c", sd_q23_2, -0.5),
  rating_simple("q23_4_c", sd_q23_4, 0.5)
)

write_csv(rating_simple_all, file.path(output_dir, "rating_simple_effects.csv"))
rating_simple_all
```

## 5.3 Direction dependence by rating

```{r rating-direction-differences}
rating_dirdiff <- function(moderator, moderator_sd, graph_keep) {
  at <- list(direction_c = c(-0.5, 0.5), graph_c = c(-0.5, 0.5), abs_slope_c = 0)
  at[[moderator]] <- c(-moderator_sd, moderator_sd)
  for (variable in c("q23_2_c", "q23_4_c", "q23_10_c")) {
    if (variable != moderator) at[[variable]] <- 0
  }

  emm <- emmeans(
    m_full,
    as.formula(paste("~ targetQuadrant | direction_c * graph_c *", moderator)),
    at = at
  )

  contrasts_by_cell <- contrast(
    emm,
    method = list(
      Vertical = c(-0.5, -0.5, 0.5, 0.5),
      Horizontal = c(-0.5, 0.5, -0.5, 0.5)
    ),
    by = c("direction_c", "graph_c", moderator)
  )

  out <- as.data.frame(
    summary(pairs(contrasts_by_cell, simple = "direction_c"), infer = c(TRUE, TRUE))
  )
  out <- out[out$graph_c == graph_keep, ]
  out$Rating <- ifelse(out[[moderator]] > 0, "High", "Low")
  out$rating_variable <- moderator
  out
}

rating_dirdiff_all <- bind_rows(
  rating_dirdiff("q23_2_c", sd_q23_2, -0.5),
  rating_dirdiff("q23_4_c", sd_q23_4, 0.5)
)

write_csv(
  rating_dirdiff_all,
  file.path(output_dir, "rating_direction_differences.csv")
)
rating_dirdiff_all
```

## 5.4 Rating figures

```{r rating-figure-functions}
rating_diff <- function(moderator, moderator_sd, graph_keep) {
  at <- list(direction_c = c(-0.5, 0.5), graph_c = c(-0.5, 0.5), abs_slope_c = 0)
  at[[moderator]] <- c(-moderator_sd, moderator_sd)
  for (variable in c("q23_2_c", "q23_4_c", "q23_10_c")) {
    if (variable != moderator) at[[variable]] <- 0
  }

  emm <- emmeans(
    m_full,
    as.formula(paste("~ targetQuadrant | direction_c * graph_c *", moderator)),
    at = at
  )
  emm_ms <- regrid(update(emm, tran = "log"), transform = "response")

  out <- as.data.frame(summary(contrast(
    emm_ms,
    method = list(
      Vertical = c(-0.5, -0.5, 0.5, 0.5),
      Horizontal = c(-0.5, 0.5, -0.5, 0.5),
      Diagonal = c(0.5, -0.5, -0.5, 0.5)
    ),
    by = c("direction_c", "graph_c", moderator)
  ), infer = c(TRUE, FALSE)))

  names(out)[names(out) %in% c("asymp.LCL", "lower.CL")] <- "lo"
  names(out)[names(out) %in% c("asymp.UCL", "upper.CL")] <- "hi"
  out <- out[out$graph_c == graph_keep, ]
  out$Direction <- factor(
    ifelse(out$direction_c > 0, "Increasing", "Decreasing"),
    levels = c("Decreasing", "Increasing")
  )
  out$Graph <- factor(
    ifelse(out$graph_c > 0, "Scatter", "Bar"),
    levels = c("Bar", "Scatter")
  )
  out$Rating <- factor(
    ifelse(out[[moderator]] > 0, "High", "Low"),
    levels = c("Low", "High")
  )
  out
}

rating_plot_data <- bind_rows(
  rating_diff("q23_2_c", sd_q23_2, -0.5),
  rating_diff("q23_4_c", sd_q23_4, 0.5)
)

diff_plot_rating <- function(data, y_label) {
  ggplot(data, aes(Direction, estimate, colour = Rating, group = Rating)) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.6) +
    geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.08, linewidth = 0.6) +
    scale_y_continuous(breaks = scales::breaks_width(50)) +
    scale_colour_manual(values = c("Low" = "#4C9A2A", "High" = "#6A3D9A")) +
    labs(x = "Trend direction", y = y_label, colour = "Graph rating") +
    theme_bw(base_size = 12)
}
```

```{r rating-vertical-figure, fig.width=6.5, fig.height=3.5}
rating_vertical_plot <- diff_plot_rating(
  subset(rating_plot_data, contrast == "Vertical"),
  "Upper - lower (ms)"
) + facet_wrap(~ Graph)
rating_vertical_plot
```

```{r rating-horizontal-figure, fig.width=6.5, fig.height=3.5}
rating_horizontal_plot <- diff_plot_rating(
  subset(rating_plot_data, contrast == "Horizontal"),
  "Right - left (ms)"
) + facet_wrap(~ Graph)
rating_horizontal_plot
```

```{r rating-diagonal-figure, fig.width=6.5, fig.height=3.5}
rating_diagonal_plot <- diff_plot_rating(
  subset(rating_plot_data, contrast == "Diagonal"),
  "LL + UR minus LR + UL (ms)"
) + facet_wrap(~ Graph)
rating_diagonal_plot
```

# 6. Session information

```{r session-information}
sessionInfo()
```
